Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-08-21 manuscripts/manuscript.Rmd
edits from paul

library("rmarkdown")
library("pdgControl")
library("reshape2")
library("plyr")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
library("snowfall")

@@

where $E_t$ represents fishing effort. We assume catch is proportional
to stock size and effort expended fishing that year, $h_t = q E_t N_t$ and
constant $q>0$ is the catchability coefficient. In
Eqn. \eqref{eq:annual_netrevenue}, $p$ is the price per unit harvest and
$c_0$ the cost of fishing and, to simplify the presentation of results,
we assume that these are constants with $p>0$ and $c_0>0$. (Examples
shown here use $p$= `r price` and $c_0$ = `r c0`.  Sensitivity analysis appears
in the supplement, along with complete R code to replicate and further 
vary the setup).

@@

Figure 2 shows the calibration graphically. Each curve plots the change
in maximum expected NPV for a given penalty function as the penalty cost
parameter is increased. In each case, the figure shows maximum expected
NPV with policy adjustment costs as a proportion of the maximum expected
NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
adjustment costs.

@@

To compare the impact of penalty functions on optimal management across
the different functional forms, we select penalty cost coefficients that
induce the same reduction in maximum expected NPV. For example, the
dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$,
for each penalty function, such that the fishery is worth `r 100*(1-reduction)`% of its
unconstrained value when optimally managed.

We focus our examination of the models on how the type and severity of
policy adjustment costs affects the optimal management strategy. To
simplify presentation of the results, we will illustrate cases where the
growth parameters are chosen so that the intrinsic rate of increase of
the fish population is 1 and the equilibrium biomass for the equivalent
deterministic model without harvesting is 10; (specifically, $A=$ `r pars[1]` and
$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}. To characterize environmental variability, we
assume multiplicative shock $Z_t$ is distributed log-normally with 
log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.

@@

Figure 3 illustrates how the different forms of adjustment cost can impact
the optimal harvest policy. Corresponding stock sizes, which are measured
here before harvest ($h_t$ being determined after observing stock size
$x_t$) and thus show less influence of the policy cost can be seen in the
supplement.  Each panel is generated against the same sequence of random
shocks so that they can be compared directly.  The harvest policy chosen
shows a systematic deviations from the penalty free optimum, depending on
the nature of the cost.  In each case, the optimal solution without any
adjustment cost is shown in against the policy induced by optimization
under the given adjustment penalty (equivalent to a `r 100*reduction`%
reduction in maximum expected NPV) is overlaid in blue.

@@

```{r Figure_S1, dev=c('pdf', 'svg')}
ex <- dt_quad %>% 
  filter(replicate=="rep_17" & time < 20) %>%
  select(time, harvest, harvest_alt) %>%
  gather(variable, stock, -time) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)"))), 
                       name="")

@@

@@

fig1s_df <- as.data.frame(subset(dt, replicate %in% paste0('rep_', 11:20)))
fig1s_df <- fig1s_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn", "replicate")]
fig1s_df <- melt(fig1s_df, id = c("time", "penalty_fn", "replicate"))
fig1s_df <- data.frame(fig1s_df, baseline = fig1s_df$variable)
variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
fig1s_df$variable <- variable_map[fig1s_df$variable]
fig1s_df$baseline <- baseline_map[fig1s_df$baseline]

fig1s_df <- subset(fig1s_df, variable=="harvest")
labeller <- function(variable,value){
if (variable=='penalty_fn') {
    return(relabel[value])
  } else {
    return(value)
  }
}

ggplot(fig1s_df, aes(time, value, col=baseline)) +
  geom_line(lwd=1) +
  facet_grid(replicate ~ penalty_fn, labeller=labeller) + 
  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  
write.csv(fig1s_df, "components/data/figure_s1.csv")

```{r Figure_S3, dependson="tidy", fig.cap="Example realization of resulting fish stock sizes under the different functional forms of adjustment costs, corresponding to policies shown in Figure 3.  Because stock sizes are measured before harvests, the effect of the penalty on the stock size is not as pronounced.", fig.height=3, fig.width=8, cache = fig.cache, dev=c("pdf", "svg", "png")}

ggplot(fishstock_fig3, aes(time, value, col=baseline)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")

write.csv(fishstock_fig3, "components/data/figure_s2.csv")
```

<!-- Ingoring this, not useful-->
```{r Table1, results="asis", eval=FALSE}
caption = "Table 1: Column 'ignoring' shows the results of ignoring a adjustment penalty when it is present, Column 'assuming' shows the results of assuming an adjustment cost when it is absent. Values (ignoring, assuming) are given as the expected net present value (ENPV) as a fraction of that when no penalty is present, ENPV0.  Percent reduction refers to penalty coefficient being calibrated to achieve the given percent reduction relative to ENPV0 when the penalty is optimally accounted for.  Comparing the second and third columns shows that ignoring a real cost is a significantly graver error, particularly in the case of quadratic costs."
pandoc.table(table1, caption=caption)
```

```{r Figure_5_alt, fig.cap="**Alternate Figure 5**.  Distribution of profits from fishing and costs paid to adjustment.  Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.  In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=3, fig.height=5, dependson="histogram-calc", dev=c("pdf", "svg", "png")}

hist_dat_alt <- melt(cbind(profits, costs = costs$V1, 
                       reed_profits = reed_profits$profits, reed_costs = reed_costs$V1),
                 id = c("penalty_fn", "replicate"))

ggplot(hist_dat_alt) + 
  geom_density(aes(value, fill=variable, color=variable), alpha=0.8)+
  facet_grid(penalty_fn~., labeller = labeller)

>>>>

library("rmarkdown")
library("pdgControl")
library("reshape2")
library("plyr")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
library("snowfall")
library("tidyr")
library("dplyr")

@@

where $E_t$ represents fishing effort. We assume catch is proportional
to stock size and effort expended fishing that year, $h_t = q E_t N_t$ and
constant $q>0$ is the catchability coefficient. In
Eqn. \eqref{eq:annual_netrevenue}, $p$ is the price per unit harvest and
$c_0$ the cost of fishing and, to simplify the presentation of results,
we assume that these are constants with $p>0$ and $c_0>0$.

To simplify presentation of the results, we will illustrate cases where the
growth parameters are chosen so that the intrinsic rate of increase of
the fish population is 1 and the equilibrium biomass for the equivalent
deterministic model without harvesting is 10; (specifically, $A=$ `r pars[1]` and
$B=$ `r pars[2]` in Eqn \eqref{eq:state_equation}. To characterize environmental variability, we
assume multiplicative shock $Z_t$ is distributed log-normally with 
log standard deviation $\sigma_g$ = `r sigma_g`. In addition, we
show cases where $p=$ `r price`, $\delta=$ `r delta` and $c_0=$ `r c0`.

Sensitivity analysis appears
in the supplement, along with complete R code to replicate and further 
vary the setup).

@@

Figure 2 shows the calibration graphically. Each curve plots the change
in maximum expected NPV for a given penalty function as the penalty cost
parameter is increased. In each case, the figure shows maximum expected
NPV with policy adjustment costs as a proportion of the maximum expected
NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
adjustment costs. The $c_i$ values are given in Table 1.

```{r table_1, results="asis"}
pandoc.table(print_npv)
```

@@

To compare the impact of penalty functions on optimal management across
the different functional forms, we select penalty cost coefficients that
induce the same reduction in maximum expected NPV. For example, the
dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$,
for each penalty function, such that the fishery is worth `r 100*(1-reduction)`% of its
unconstrained value when optimally managed. We focus our examination of the models on how the type and severity of policy adjustment costs affects the optimal management strategy.

@@

Figure 3 illustrates how the different forms of adjustment cost can impact
the optimal harvest policy. Corresponding stock sizes can be seen in the
supplement.  Each panel is generated against the same sequence of random
shocks so that they can be compared directly.  The harvest policy chosen
shows a systematic deviations from the penalty free optimum, depending on
the nature of the cost.  In each case, the optimal solution without any
adjustment cost is shown in against the policy induced by optimization
under the given adjustment penalty (equivalent to a `r 100*reduction`%
reduction in maximum expected NPV) is overlaid in blue.

@@

```{r Figure_S1, dev=c('pdf', 'svg')}

labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))

ex <- dt_quad %>% 
  filter(replicate=="rep_17" & time < 20) %>%
  select(time, harvest, harvest_alt) %>%
  gather(variable, stock, -time) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=labels, 
                       name="")

@@

Recall that in our model definition, stock sizes are measured before harvest ($h_t$ being determined after observing stock size
$x_t$) and thus show less influence of the policy cost than the harvest itself.

@@

labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[1-3]))), 
            harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
            fishstock = substitute(paste("Stock dynamics under under ", paste(Pi[1-3]))), 
            alternate = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")
ex <- dt %>% 
  filter(replicate %in% paste0("rep_", 10:20) & penalty_fn == "L1" & time < 20) %>%
  select(time, fishstock, harvest, alternate, harvest_alt) %>%
  gather(variable, stock, -time, -replicate)

ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=labels, name="") +  
  facet_wrap(~replicate)

write.csv(ex, "components/data/figure_s2.csv")
```
